Examination of shapes! (homework exam)

### 2016-02-23 geometricAlgorithms/homeworkExam/homeworkExam.tex
having a nice triangle
completly overdid the first question...

\begin{pspicture}(-2,-2)(3,3)
\psset{viewpoint=100 30 20,Decran=100}
\axesIIID[showOrigin=false](1,1,1)(3,2,2.5)
\psSolid[object=new,
        action=draw,
        sommets=
		0 2 0
		-2 0 -2
		2 0 -2
		2 0 2
   faces={
       [0 1 2]
       [0 2 3]
       [0 3 1]
       [1 2 3]
       }]%
\end{pspicture}

@@

\section{Red and blue lines}
\subsection{The status structure}
A binary tree sorted on the x axis.
\subsection{Initialization}

>>>>

\begin{figure}
\begin{pspicture}(-2,-2)(3,3)
\psset{viewpoint=100 0 30,Decran=100}
\psSolid[object=tetrahedron,
		r=2,
		RotZ=65,
		fillcolor=magenta!20,
        action=draw**,
		numfaces=all]%
\psSolid[object=tetrahedron,
		r=2,
		RotZ=125,
		fillcolor=magenta!20,
        action=draw**,
		numfaces=all](0, 4, 0)%
\psSolid[object=tetrahedron,
		r=2,
		RotZ=185,
		fillcolor=magenta!20,
        action=draw**,
		numfaces=all](0, 8, 0)%
\end{pspicture}

\caption{Not unique}
\end{figure}
\newpage

\begin{pspicture}(-2,-2)(3,3)
\psset{viewpoint=100 0 0,Decran=100}
\psSolid[object=new,
        action=draw**,
		fillcolor=cyan,
		numfaces=all,
        sommets=
		0 0 2
		-1.5 -0.1 0
		1 -1 0
		1.5 1.5 0,
   faces={
       [0 1 2]
       [0 2 3]
       [0 3 1]
       [1 3 2]}](0,0,0)%
\psSolid[object=new,
        action=draw**,
		fillcolor=cyan,
		RotZ=65,
		numfaces=all,
        sommets=
		0 0 2
		-1.5 -0.1 0
		1 -1 0
		1.5 1.5 0,
   faces={
       [0 1 2]
       [0 2 3]
       [0 3 1]
       [1 3 2]}](0,4,0)%
\psSolid[object=new,
        action=draw**,
		fillcolor=cyan,
		RotZ=125,
		numfaces=all,
        sommets=
		0 0 2
		-1.5 -0.1 0
		1 -1 0
		1.5 1.5 0,
   faces={
       [0 1 2]
       [0 2 3]
       [0 3 1]
       [1 3 2]}](0,8,0)%
	   %%%%%%%%%%%%%%%% X
\psSolid[object=new,
        action=draw**,
		fillcolor=cyan,
		numfaces=all,
        sommets=
		0 0 2
		-1.5 -0.1 0
		1 -1 0
		1.5 1.5 0,
   faces={
       [0 1 2]
       [0 2 3]
       [0 3 1]
       [1 3 2]}](0,0,-4)%
\psSolid[object=new,
        action=draw**,
		fillcolor=cyan,
		RotX=65,
		numfaces=all,
        sommets=
		0 0 2
		-1.5 -0.1 0
		1 -1 0
		1.5 1.5 0,
   faces={
       [0 1 2]
       [0 2 3]
       [0 3 1]
       [1 3 2]}](0,4,-4)%
\psSolid[object=new,
        action=draw**,
		fillcolor=cyan,
		RotX=120,
		numfaces=all,
        sommets=
		0 0 2
		-1.5 -0.1 0
		1 -1 0
		1.5 1.5 0,
   faces={
       [0 1 2]
       [0 2 3]
       [0 3 1]
       [1 3 2]}](0,8,-4)%
	   %%%%%%%%%%%%%%%% Y
\psSolid[object=new,
        action=draw**,
		fillcolor=cyan,
		numfaces=all,
        sommets=
		0 0 2
		-1.5 -0.1 0
		1 -1 0
		1.5 1.5 0,
   faces={
       [0 1 2]
       [0 2 3]
       [0 3 1]
       [1 3 2]}](0,0,-8)%
\psSolid[object=new,
        action=draw**,
		fillcolor=cyan,
		RotY=85,
		numfaces=all,
        sommets=
		0 0 2
		-1.5 -0.1 0
		1 -1 0
		1.5 1.5 0,
   faces={
       [0 1 2]
       [0 2 3]
       [0 3 1]
       [1 3 2]}](0,4,-8)%
\psSolid[object=new,
        action=draw**,
		fillcolor=cyan,
		RotY=125,
		numfaces=all,
        sommets=
		0 0 2
		-1.5 -0.1 0
		1 -1 0
		1.5 1.5 0,
   faces={
       [0 1 2]
       [0 2 3]
       [0 3 1]
       [1 3 2]}](0,8,-8)%
\end{pspicture}

@@

\section{Red and blue lines}
\subsection{The status structure}
A binary tree sorted on the x axis.
The event list is a structure of 
\subsection{Initialization}
